Chemical composition analysis for X-ray transport container scans.

### 2018-10-03 EMIN-2018/presentation/main.tex
save'

                \end{itemize}
            \end{column}
            \begin{column}{0.4\textwidth} 
        \includegraphics[width=1\textwidth]{figures/terrorist.jpg}
            \end{column}
        \end{columns}  
    \end{frame}
    \begin{frame}
    \frametitle{Methodology: Gamma ray attenuation}
    \begin{columns}
        \begin{column}{0.7\textwidth}
            $$
            T(E_0, t, z) = \frac{\int \limits_0^{E_0} S(E_0, E) \exp(-\mu(E,z)\times t)~dE)}{\int \limits_0^{E_0} S(E_0, E)~dE}
            $$
%            \hline
            \includegraphics[width=1\textwidth]{figures/Attenuation.pdf}
        \end{column}
    \vline~
        \begin{column}{0.4\textwidth} 
            $T$ -  transmittance\\
            $S(E_0, E)$ - response function\\
            $\mu(E,z)$ - attenuation\\
            $t$ -  optical thickness\\
            $E_0$ -  up-limit energy of bremsstrahlung\\
            $E$ - energy of gamma ray\\
            $z$ - charge of nuclei 
%            \hline
            \includegraphics[width=1\textwidth]{figures/Bremsstrahlung.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Methodology: Existing solution}
    \begin{block}{Dual energy method}%<1>

        $$
        F(z) = \frac{|t(E^{(1)}_0,z) - t(E^{(2)}_0,z)|}{t(E^{(1)}_0,z)} \to min
        $$
    \end{block}

@@

\begin{frame}
    \frametitle{Methodology: Disadvantages and proposition}
    \begin{block}{Disadvantages of dual energy method}%<1>
        \begin{itemize}
            \item It is difficult expose on the target with beams with different energy.
            \item Low efficiency for target which contain elements with strongly differing charges
        \end{itemize}
    \end{block}
    \begin{block}{Our proposition}%<2>
        \begin{itemize}
            \item Use only one electron beam with energy 10 MeV.
            \item Measure not only space distribution, but also energy of gamma ray.
        \end{itemize}
    \end{block}
\end{frame}
%-------------Моделирование 1 часть -------------------
    \begin{frame}
    \frametitle{Simulation: First schema}
    \begin{columns}
%        \begin{column}{0.4\textwidth}
%            \begin{itemize}
%                \item 
%                \item 
%                \item 
%                
%            \end{itemize}
%        \end{column}
        \begin{column}{1\textwidth} 
            \includegraphics[width=1\textwidth]{figures/yed_schema_1.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Some examples}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            Very dangerous item\\
            \includegraphics[width=1\textwidth]{figures/Sword.pdf}
        \end{column}
        \begin{column}{0.5\textwidth}
            Uranium cube ( 6cm) in lead sphere (thickness - 1 cm)\\
            \includegraphics[width=1\textwidth]{figures/sim_cube_in_orb.jpeg}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Some examples}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \centering Explosive search\\
            \includegraphics[width=1\textwidth]{figures/sim_hexogen.jpeg}

        \end{column}
        \begin{column}{0.5\textwidth}
            Comparison of energy spectrum for aluminium and uranium orb.\\
            \includegraphics[width=1\textwidth]{figures/Difference.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Some examples}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            Energy deposit in detector cells for several material\\
            \includegraphics[width=1\textwidth]{figures/sim_1.jpeg}

@@

            \includegraphics[width=1\textwidth]{figures/sim_2.jpeg}
        \end{column}
    \end{columns}  
\end{frame}
%-------------Моделирование, часть 2 --------------------------

@@

            \includegraphics[width=1\textwidth]{figures/setup1.png}
        \end{column}
                \begin{column}{0.5\textwidth}
            \includegraphics[width=1\textwidth]{figures/yed.pdf}
        \end{column}
    \end{columns}  
\end{frame}

@@

    \begin{columns}
    \begin{column}{0.5\textwidth}
        $^{137}Cs$ --- $0.662~MeV$\\
        \includegraphics[width=1\textwidth]{figures/setup2.png}
    \end{column}
    \begin{column}{0.5\textwidth}
                Sum of signals from 2 photodiode\\
                Noise threshold: 100 KeV\\
        \begin{tabular}[c]{|c|c|}
             \hline 
            Energy, MeV & Sigma/Mean \\
            \hline 
           0.511 & 14.7\%  \\ 
            \hline 
            0.662 & 19\%\\ 
            \hline 
            1.275 & 13\%\\
            \hline 
        \end{tabular} 
\\

>>>>

                \end{itemize}
            \end{column}
            \begin{column}{0.4\textwidth} 
        \includegraphics[width=1\textwidth]{figures/terrorist.jpg}
            \end{column}
        \end{columns}  
    \end{frame}
    \begin{frame}
    \frametitle{Methodology: Gamma ray attenuation}
    \begin{columns}
        \begin{column}{0.7\textwidth}
            $$
            T(E_0, t, Z) = \frac{\int \limits_0^{E_0} S(E_0, E) \exp(-\mu(E,Z)\times t)~dE)}{\int \limits_0^{E_0} S(E_0, E)~dE}
            $$
%            \hline
            \includegraphics[width=1\textwidth]{figures/Attenuation.pdf}
        \end{column}
    \vline~
        \begin{column}{0.4\textwidth} 
            $T$ -  transmittance\\
            $S(E_0, E)$ - response function\\
            $\mu(E,Z)$ - attenuation\\
            $t$ -  optical thickness\\
            $E_0$ -  up-limit energy of bremsstrahlung\\
            $E$ - energy of gamma ray\\
            $Z$ - charge of nuclei 
%            \hline
            \includegraphics[width=1\textwidth]{figures/Bremsstrahlung.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Methodology: Existing solution}
    \begin{block}{Dual energy method}%<1>
        \begin{itemize}
            \item We can't defined Z if optical thickness $t$ is unknown.
            \item But we can use two electron beam with differing energy which give gamma ray with up-limit energy $E^{(1)}_0$ and $E^{(2)}_0$.
            \item Then we can get Z as result of minimizing this function:
            $$
            F(z) = \frac{|t(E^{(1)}_0,z) - t(E^{(2)}_0,z)|}{t(E^{(1)}_0,z)} \to min
            $$
            \item This technique allow to carry scan object to one of four groups: $Z_{eff} \sim 5$, $Z_{eff} \sim 13$, $Z_{eff} \sim 26$, $Z_{eff} \sim 82$.
        \end{itemize}

    \end{block}

@@

\begin{frame}
    \frametitle{Methodology: Disadvantages and proposition}
    \begin{block}{Disadvantages of dual energy method}%<1>
        \begin{itemize}
            \item It is difficult expose on the target with beams with different energy.
            \item Low efficiency for target which contain elements with strongly differing charges
        \end{itemize}
    \end{block}
    \begin{block}{Our proposition}%<2>
        \begin{itemize}
            \item Use only one electron beam with energy 10 MeV.
            \item Measure not only space distribution, but also energy of gamma ray.
        \end{itemize}
    \end{block}
\end{frame}
%-------------Моделирование 1 часть -------------------
    \begin{frame}
    \frametitle{Simulation: Preliminary estimates}
    \begin{columns}
%        \begin{column}{0.4\textwidth}
%            \begin{itemize}
%                \item 
%                \item 
%                \item 
%                
%            \end{itemize}
%        \end{column}
        \begin{column}{1\textwidth} 
            \includegraphics[width=1\textwidth]{figures/yed_schema_1.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Preliminary estimates}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            Very dangerous item\\
            \includegraphics[width=1\textwidth]{figures/Sword.pdf}
        \end{column}
        \begin{column}{0.5\textwidth}
            Uranium cube ( 6cm) in lead sphere (thickness - 1 cm)\\
            \includegraphics[width=1\textwidth]{figures/sim_cube_in_orb.jpeg}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Preliminary estimates}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \centering Explosive search\\
            \includegraphics[width=1\textwidth]{figures/sim_hexogen.jpeg}

        \end{column}
        \begin{column}{0.5\textwidth}
            Comparison of energy spectrum for aluminium and uranium orb (radius - 1 cm).\\
            \includegraphics[width=1\textwidth]{figures/Difference.pdf}
        \end{column}
    \end{columns}  
\end{frame}

\begin{frame}
    \frametitle{Simulation: Preliminary estimates}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            Energy deposit in detector cells for several material\\
            \includegraphics[width=1\textwidth]{figures/sim_1.jpeg}

@@

            \includegraphics[width=1\textwidth]{figures/sim_2.jpeg}
        \end{column}
    \end{columns}  
\end{frame}
%-------------Моделирование, часть 2 --------------------------
    \begin{frame}
    \frametitle{Simulation: Thickness reconstruction}
    \begin{columns}
        %        \begin{column}{0.4\textwidth}
        %            \begin{itemize}
        %                \item 
        %                \item 
        %                \item 
        %                
        %            \end{itemize}
        %        \end{column}
        \begin{column}{1\textwidth} 
            \includegraphics[width=1\textwidth]{figures/yed_schema_2.pdf}
        \end{column}
    \end{columns}  
\end{frame}

    \begin{frame}
        %3d -томография
    \frametitle{Simulation: Perspectives}
    \begin{columns}
                \begin{column}{0.6\textwidth}
                    \begin{itemize}
                        \item 
                        \item 
                        \item

                    \end{itemize}
                \end{column}
    \end{columns}  
\end{frame}

@@

            \includegraphics[width=1\textwidth]{figures/setup1.png}\\
            Experiment was conduct by Dr. Guber and Dr. Ivashkin.
        \end{column}
                \begin{column}{0.5\textwidth}
            \includegraphics[width=1\textwidth]{figures/yed.pdf}
        \end{column}
    \end{columns}  
\end{frame}

@@

    \begin{columns}
    \begin{column}{0.5\textwidth}
        $^{137}Cs$ --- $0.662~MeV$\\
        \includegraphics[width=1\textwidth]{figures/setup2.png}
    \end{column}
    \begin{column}{0.5\textwidth}
                Sum of signals from 2 photodiode\\
                Noise threshold: 100 KeV\\
                ~\\
        \begin{tabular}[c]{|c|c|}
             \hline 
            Energy, MeV & Sigma/Mean \\
            \hline 
           0.511 & 14.7\%  \\ 
            \hline 
            0.662 & 19\%\\ 
            \hline 
            1.275 & 13\%\\
            \hline 
        \end{tabular} 
\\
